What's hot and what's not:\\Windowed developer topic analysis

### 2010-01-29 icpc/icpc2010.tex
Added table with automated labeling results.

\begin{table*}[h]
	\caption{Results for automatic topic labeling}
	\centering
	\label{tbl:wordlist}
\begin{tabular}{c|c|c|c}
\toprule
Measure &		 \textsf{exp1} &	 \textsf{exp2} &	 \textsf{exp3} \\
\midrule
Topics &			500		 &			500  	 & 		500  \\
Named topics &		281      &			125      &		328  \\
Unnamed topics &	139      &			295      &      92   \\
\bottomrule
\end{tabular}
\end{table*}

@@

\subsubsection{Analysing the unsupervised labeling}
Based on the labels, and our manual topic labeling, we compared the results of the unsupervised word matching approach. For each quality we tried to assess whether the manual tag matched the unsupervised label assigned. Table \ref{tbl:maxdb-unsup-results} shows our results for MaxDB.

>>>>

\begin{table*}[h]
	\caption{Automatic topic labeling}
	\centering
	\label{tbl:wordlist}
\begin{tabular}{c|c|c|c}
\toprule
Measure &		 \textsf{exp1} &	 \textsf{exp2} &	 \textsf{exp3} \\
\midrule
Topics &			500		 &			500  	 & 		500  \\
Named topics &		281      &			125      &		328  \\
Unnamed topics &	139      &			295      &      92   \\
\bottomrule
\end{tabular}
\end{table*}

@@

\subsubsection{Analysing the unsupervised labeling}
Based on the labels, and our manual topic labeling, we compared the results of the unsupervised word matching approach. For each quality we tried to assess whether the manual tag matched the unsupervised label assigned. Table \ref{tbl:maxdb-unsup-results} shows our results for MaxDB. In general results are poor. Using the F-Measure, the weighted average of precision and recall, where 1 is perfect, our best results are 0.6, a few at 0.4, and most around 0.2. Similar results using the Matthew's correlation coefficient (used to measure efficacy where classes are of different sizes), and the receiver operating characteristic area under curve.

\begin{table*}[h]
	\caption{Results for automatic topic labeling. f1 = f-measure, mcc = Matthew's correlation coeff., roca = ROC area}
	\centering
	\label{tbl:maxdb-unsup-results}
\begin{tabular}{c|c|c|c|c|c|c}
\toprule
Experiment & label & f1 & mcc & precision & recall & roca  \\ 
\midrule
MaxDB exp2 & portability & 0.228 & 0.182 & 0.520 & 0.146 & 0.553 \\ 
 & efficiency & 0.217 & 0.125 & 0.237 & 0.200 & 0.558\\ 
 & reliability & 0.380 & 0.340 & 0.246 & 0.829 & 0.765 \\ 
 & functionality & 0.095 & 0.083 & 0.250 & 0.059 & 0.521 \\ 
 & maintainability & 0.092 & 0.123 & 0.571 & 0.050 & 0.520 \\ 
 & usability & 0.175 & 0.138 & 0.113 & 0.389 & 0.620 \\ 
 & total & 0.236 & 0.127 & 0.248 & 0.225 & 0.561 \\ 
\midrule
mysql exp2 & portability & 0.138 & 0.211 & 1.000 & 0.074 & 0.537 \\ 
 & efficiency & 0.345 & 0.327 & 0.476 & 0.270 & 0.625 \\ 
 & reliability & 0.425 & 0.287 & 0.348 & 0.545 & 0.669 \\ 
 & functionality & 0.025 & 0.006 & 0.571 & 0.013 & 0.501 \\ 
 & maintainability & 0.000 & 0.000 & 0.000 & 0.000 & 0.500 \\ 
 & usability & 0.175 & 0.135 & 0.200 & 0.156 & 0.560 \\ 
 & total & 0.167 & 0.095 & 0.403 & 0.105 & 0.527 \\ 
\midrule
maxdb exp3 & portability & 0.472 & 0.286 & 0.402 & 0.573 & 0.660 \\ 
 & efficiency & 0.223 & 0.068 & 0.130 & 0.778 & 0.549 \\ 
 & reliability & 0.257 & 0.196 & 0.149 & 0.927 & 0.652 \\ 
 & functionality & 0.236 & 0.187 & 0.138 & 0.824 & 0.665 \\ 
 & maintainability & 0.338 & 0.112 & 0.266 & 0.463 & 0.566 \\ 
 & usability & 0.108 & 0.094 & 0.057 & 0.944 & 0.595 \\ 
 & total & 0.258 & 0.093 & 0.160 & 0.671 & 0.568 \\ 
\midrule
mysql exp3 & portability & 0.413 & 0.170 & 0.564 & 0.325 & 0.574 \\ 
 & efficiency & 0.158 & 0.105 & 0.089 & 0.703 & 0.608 \\ 
 & reliability & 0.388 & 0.240 & 0.260 & 0.758 & 0.660 \\ 
 & functionality & 0.652 & 0.240 & 0.655 & 0.649 & 0.620 \\ 
 & maintainability & 0.203 & 0.007 & 0.240 & 0.175 & 0.503 \\ 
 & usability & 0.105 & 0.013 & 0.057 & 0.688 & 0.513 \\ 
 & total & 0.362 & 0.076 & 0.284 & 0.499 & 0.544 \\
\bottomrule
\end{tabular}
\end{table*}

### 2010-01-29 lda-experiment.tex
misc changes to text
Added table with automated labeling results.

We ran it and we found that wordnet generated word lists for
\emph{correctness} were too large andgeneric. Results are listed below
in the results section

@@

Now wordlists that were correlated with each other
correctness, interoperability 1
efficiency, performance 1
efficiency, security 1
efficiency, testability 1
efficiency, verifiability 1
integrity, traceability 1
integrity, verifiability 1
interoperability, interoperability 1
modularity, performance 1
performance, security 1
performance, usability 1
traceability, understandability 1
traceability, usability 1
understandability, verifiability 1
efficiency, traceability 2
security, testability 2
testability, usability 2
accuracy, accuracy 3
accuracy, correctness 3
accuracy, testability 3
accuracy, understandability 3
integrity, testability 3
correctness, integrity 4
security, verifiability 4
usability, usability 4
correctness, efficiency 5
correctness, modularity 5
correctness, security 5
correctness, understandability 5
modularity, modularity 5
security, traceability 5
testability, understandability 5
understandability, understandability 6
efficiency, efficiency 8
security, security 8
integrity, integrity 9
performance, traceability 10
performance, verifiability 12
performance, testability 17
correctness, performance 24
testability, verifiability 26
testability, traceability 32
performance, performance 58
correctness, testability 62
correctness, verifiability 76
traceability, verifiability 76
verifiability, verifiability 78
correctness, traceability 86
traceability, traceability 95
testability, testability 121
correctness, correctness 182
\end{verbatim}

>>>>

We ran it and we found that wordnet generated word lists for
\emph{correctness} were too large and generic. Results are listed below
in the results section

@@

Now wordlists that were correlated with each other
correctness, interoperability 1
efficiency, performance 1
efficiency, security 1
efficiency, testability 1
efficiency, verifiability 1
integrity, traceability 1
integrity, verifiability 1
interoperability, interoperability 1
modularity, performance 1
performance, security 1
performance, usability 1
traceability, understandability 1
traceability, usability 1
understandability, verifiability 1
efficiency, traceability 2
security, testability 2
testability, usability 2
accuracy, accuracy 3
accuracy, correctness 3
accuracy, testability 3
accuracy, understandability 3
integrity, testability 3
correctness, integrity 4
security, verifiability 4
usability, usability 4
correctness, efficiency 5
correctness, modularity 5
correctness, security 5
correctness, understandability 5
modularity, modularity 5
security, traceability 5
testability, understandability 5
understandability, understandability 6
efficiency, efficiency 8
security, security 8
integrity, integrity 9
performance, traceability 10
performance, verifiability 12
performance, testability 17
correctness, performance 24
testability, verifiability 26
testability, traceability 32
performance, performance 58
correctness, testability 62
correctness, verifiability 76
traceability, verifiability 76

\end{verbatim}
